An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
tweaks

Lemma~\ref{lem:X} now allows us to observe the relationship between embeddings, finite representative sets and polyhedral Bayes risks; we later expand on this relationship in Propositions~\ref{prop:embed-bayes-risks} and \ref{prop:embed-iff-trims-equal}.
%As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by Proposition~\ref{prop:representative-embeds-restriction}.
\begin{corollary}\label{cor:poly-risk-fin-rep}
  The following are equivalent for any minimizable loss $L:\reals^d\to\reals^\Y_+$.
  \begin{enumerate}
  \item $\risk{L}$ is polyhedral.
  \item $L$ has a finite representative set.
  \item $L$ embeds a discrete loss.
  \end{enumerate}
\end{corollary}
\begin{proof}
	If $\risk L$ is polyhedral, then Lemma~\ref{lem:X} implies that $L$ has a finite representative set.
	Moreover, if $L$ has a finite representative set $\Sc$, then Proposition~\ref{prop:representative-embeds-restriction} implies that $L$ embeds $L|_{\Sc}$, which is finite.
	Lemma~\ref{lem:loss-restrict} additionally implies that $\risk L = \risk{L|_{\Sc}}$, which is polyhedral as the pointwise supremum of a finite set of affine functions.
\end{proof}

@@

An interesting direction is to understand consistent surrogates by studying their superprediction sets, as has been done for proper losses~\citep{williamson2014geometry}.
The superprediction set of a loss is the set of loss vectors weakly dominated by the range of the loss: $\{v \in \reals^\Y \mid \exists r\; L(r) \leq v\}$, where the inequality holds pointwise.
One appealing aspect of the superprediction set is that it ignores the surrogate reports and focuses directly on the set of loss vectors, in a similar fashion to the trim operation in \S~\ref{sec:trim}.
In particular, it may be that questions about the required prediction dimension (see above) could be more readily answered by trying to find low-dimensional structures in the superprediction set of the target loss.

>>>>

Lemma~\ref{lem:X} now allows us to observe the relationship between embeddings, finite representative sets and polyhedral Bayes risks; we later expand on this relationship in Propositions~\ref{prop:embed-bayes-risks} and \ref{prop:embed-iff-trims-equal}.
%As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by Proposition~\ref{prop:representative-embeds-restriction}.
\begin{corollary}\label{cor:poly-risk-fin-rep}
  The following are equivalent for any minimizable loss $L:\reals^d\to\reals^\Y_+$.
  \begin{enumerate}
  \item $\risk{L}$ is polyhedral.
  \item $L$ has a finite representative set.
  \item $L$ embeds a discrete loss.
  \end{enumerate}
\end{corollary}
\begin{proof}
	If $\risk L$ is polyhedral, then Lemma~\ref{lem:X} implies that $L$ has a finite representative set.
  For any surrogate $L$ with a finite representative set $\Sc$, Proposition~\ref{prop:representative-embeds-restriction} implies that $L$ embeds $L|_{\Sc}$, which is finite.
  Finally, if $L$ embeds a discrete loss, then by definition $L$ has a finite representative set $\Sc$, and Lemma~\ref{lem:loss-restrict} implies that $\risk L = \risk{L|_\Sc}$, which is polyhedral as the pointwise minimum of a finite set of affine functions.
\end{proof}

@@

An interesting direction is to understand consistent surrogates by studying their superprediction sets, as has been done for proper losses~\citep{williamson2014geometry}.
The superprediction set of a loss is the set of loss vectors weakly dominated by the range of the loss: $\{v \in \reals^\Y \mid \exists r\; L(r) \leq v\}$, where the inequality holds pointwise.
One appealing aspect of the superprediction set is that it ignores the surrogate reports and focuses directly on the set of loss vectors, in a similar fashion to the trim operation in \S~\ref{sec:trim}.
In particular, taking inspiration from \citet{ramaswamy2016convex}, it may be that questions about the required prediction dimension (see above) could be more readily answered by trying to find low-dimensional structures in the superprediction set of the target loss.
